\documentclass{article}

\usepackage[top=0.8in]{geometry}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{bm}
\usepackage{xcolor}
\usepackage{mathtools}
\usepackage[toc,page]{appendix}
\usepackage{titlesec}
\usepackage{bbm}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{float}
\usepackage{subcaption}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{problem}[theorem]{Problem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{example}[theorem]{Example}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{fact}[theorem]{Fact}
\newtheorem{post}[theorem]{Postulate}

\newcommand{\plot}[1]{
\begin{center}
\textcolor{blue}{\textbf{#1}}
\end{center}
}

\begin{document}
\title{SPIDER: How To Do It In Three Steps}
\maketitle
\thispagestyle{empty}
\noindent
\textbf{STEP ONE:} Back to the game.
\begin{enumerate}
	\item Rebulid the system and reproduce the results of measurements made with OSA.
	\item Reproduce the results of measurements made with APEX.
\end{enumerate}
\textbf{STEP TWO:} Verify if APEX-based SPIDER could work at all.\\ \\
\textbf{Problem:} APEX is extremely noisy for light of power $<1\mu$W and in the areas of low intensity. For instance, it cannot measure the phase jump in the middle of the first Hermite-Gaussian spectral mode.
\begin{enumerate}
	\item Consider using an erbium-doped fiber amplifier just before APEX to increase the intensity.
	\item Measure the phase jump in the area of high intensity - \emph{someone} needs to teach me how to use the pulse shaper.
	\item Make sure if it is, indeed, impossible to perform measurements with APEX with increased sensitivity (which turned out to be a gamechanger for OSA).
	\item In order to maximize the resolution try to minmize the width of the peak in the \emph{spectral phase difference} plot measured for the case of \emph{signum}-like spectral phase. Identify how does this width depend on all the other factors, particularly the value of the shear.

\end{enumerate}
\textbf{STEP THREE:} If APEX-based SPIDER could work, optimize everything.
\begin{enumerate}
	\item Change the photodiode for the AWG-generated saw-like (or slowly-varying sine) signal in order to ensure constant slope. Simulation, I coded, shows why this is crucial.
	\item Measure the dispersion of the PM fiber in order to optimize the subtraction of the parabolic phase. I want to measure the $D_\lambda$ parameter with an accuracy of 3 significant figures.
	\item Reduce the noise in the signal. Realign the axes in the EOPM to match the axes of the PM fibers in order to eliminate the oscillations with period of 65 GHz. Identify other sources of noise and try to eliminate them.
\end{enumerate}

\end{document}